No need to know: astrophysics-free gravitational-wave cosmology

### 2024-06-28 src/tex/ms.tex
[showyourwork] overleaf sync

\section{Effects of fitting for secondary mass}
\label{ap:mass ratio}
\new{We examine the effect of only fitting the distribution of primary masses on our results.
To do so, we perform two spectral siren analyses: one that includes a fit to mass ratio, and one that does not.
Both analyses use the parametric, \plp{} model for the distribution of primary masses.
We model the distribution of mass ratios with a power law, similarly to the majority of analyses presented in \citet{abbott_population_2021,abbott_population_2023}.

We use the same set of simulated events for both analyses.
These are generated in the same way as described in Section~\ref{sec:data generation}.

The results are shown in Figure~\ref{fig:mass ratio}.
We find the posteriors on \Ho{} to be similar between the two cases.
Additionally, the recovered mass spectra are nearly identical.
We therefore conclude that fitting for mass ratios does not significantly impact our main conclusions.
}
\begin{figure*}
    \includegraphics[width=\textwidth]{figures/q_comparison.pdf}
    \caption{Comparison of a parametric spectral siren analysis performed while fitting for the distributions of primary and secondary masses (magenta solid) and primary masses only (green dashed).
    The posterior on \Ho{} is relatively unchanged between the two, and only minor changes are observed in the mass spectrum.}
    \label{fig:mass ratio}
    \script{fit_q_comparison.py}
\end{figure*}

>>>>

\section{Effects of fitting for secondary mass}
\label{ap:mass ratio}
\new{We examine the effect of only fitting the distribution of primary masses on our results.
To do so, we perform two spectral siren analyses: one that includes a fit to mass ratio, and one that does not.
Both analyses use the parametric, \plp{} model for the distribution of primary masses.
We model the distribution of mass ratios with a power law, similarly to the majority of analyses presented in \citet{abbott_population_2021,abbott_population_2023}.}

\new{We use the same set of simulated events for both analyses.
These are generated in the same way as described in Section~\ref{sec:data generation}.
}

\new{The results are shown in Figure~\ref{fig:mass ratio}.
We find the posteriors on \Ho{} to be similar between the two cases.
Additionally, the recovered mass spectra are nearly identical.
We therefore conclude that fitting for mass ratios does not significantly impact our main conclusions.
}
\begin{figure*}
    \includegraphics[width=\textwidth]{figures/q_comparison.pdf}
    \caption{Comparison of a parametric spectral siren analysis performed while fitting for the distributions of primary and secondary masses (magenta solid) and primary masses only (green dashed).
    The posterior on \Ho{} is relatively unchanged between the two, and only minor changes are observed in the mass spectrum.}
    \label{fig:mass ratio}
    \script{fit_q_comparison.py}
\end{figure*}
